---
title: "Regression Models Course Project"
author: "OvieEmiri"
date: "January 3, 2016"
output: html_document
---

load mtcars dataset
```{r}
data("mtcars")
```

visualise part of mtcars

```{r}
head(mtcars)
```

boxplot to get distingusion for both transmission category
```{r}
boxplot(mpg ~ am, data = mtcars, ylim = c(0, 40),
        col = "thistle4", whisklty =1, boxwex = 0.5, staplelty = 0,
        xlab = "Transmission Category(0 = automatic, 1 = manual)",
        ylab = "Miles per Gallon", main = "MpG vs Transmission Category")
```

#Fit/Model Selection
```{r}
model <- lm(mpg ~ factor(am), data = mtcars)
coef(summary(model))
```
R^2 of 0.3598 show our model is only 35.9% explained by the regression variance in our model
Analyse other variable in the model using multiple linear regression

fit multi linear model to analyse using other variable, this we do using anova
```{r}
testing <- aov(mpg ~ ., data = mtcars)
summary(testing)
```
shows that variables: cyl, disp and wt would help fit our new model as indicated by their respective p-values. we now fit a model includin these variables

```{r}
model1 <- lm(mpg ~ factor(am) + disp + cyl + wt, data = mtcars); summary(model1)
model2 <- lm(mpg ~ factor(am) + cyl + wt, data = mtcars); summary(model2)
```
83.0% of variability is explained by the new model as compared to the previous of 35.9%

#Plotting the model
```{r}
par(mfrow = c(2, 2))
plot(model2)
```

#Conclusion
  manual transmission cars have about 1.7 mpg more than automatic transmission cars, mgp decreses with the number of cylinders: about 1.5, mpg decreases by about 3.1 for every 1000 pound increase in weight